quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays

### 2025-02-27 man/manuscript/manuscript.qmd
Updated the Quarto file to include the calculate_metrics() function.

# Calculate Key Metrics ---------------------------------------------------

mpr <- calculate_MPR(normal, data_is_norm = TRUE)
ms  <- calculate_MS(normal, data_is_norm = TRUE)
ttt <- calculate_TtT(normal, threshold = 2)

analyzed <- data.frame(
  `Sample IDs`                = meta$`Sample IDs`,
  `Dilutions`                 = meta$Dilutions,
  `Maxpoint Ratio`            = mpr,
  `Max Slope`                 = ms,
  `Time-to-Threshold`         = ttt,
  `Rate of Amyloid Formation` = 1 / ttt
)
```
\newpage

>>>>

analyzed <- calculate_metrics(normal, meta)
```
\newpage
